
## General
```{r}
df_dta %>%
  distinct(fDISEASE, fCRITERION) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE, 
              values_from = value, 
              values_fill = "") %>%
  kable(caption = "Crosstable of CRITERION vs DISEASE")

```


## Impact on autonomy
```{r}
df_dta %>%
  filter(fCRITERION == "Impact on autonomy") %>%
  distinct(fINDICATOR, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


### Mobility
```{r}
df_dta %>%
  filter(fCRITERION == "Impact on autonomy") %>%
  filter(fINDICATOR == "Mobility") %>%
  distinct(CATEGORIES, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


### Self-care
```{r}
df_dta %>%
  filter(fCRITERION == "Impact on autonomy") %>%
  filter(fINDICATOR == "Self-care") %>%
  distinct(CATEGORIES, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


### Usual activities
```{r}
df_dta %>%
  filter(fCRITERION == "Impact on autonomy") %>%
  filter(fINDICATOR == "Usual activities") %>%
  distinct(CATEGORIES, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


## Impact on general health-related quality of life
```{r}
df_dta %>%
  filter(fCRITERION == "Impact on general health-related quality of life") %>%
  distinct(fINDICATOR, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


### Associated comorbidities
```{r}
df_dta %>%
  filter(fCRITERION == "Impact on general health-related quality of life") %>%
  filter(fINDICATOR == "Associated comorbidities") %>%
  distinct(CATEGORIES, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


### EQ-5D-5L average score
```{r}
df_dta %>%
  filter(fCRITERION == "Impact on general health-related quality of life") %>%
  filter(fINDICATOR == "EQ-5D-5L average score") %>%
  distinct(CATEGORIES, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


### Years of life lived with disability (per case)
```{r}
df_dta %>%
  filter(fCRITERION == "Impact on general health-related quality of life") %>%
  filter(fINDICATOR == "Years of life lived with disability (per case)") %>%
  distinct(CATEGORIES, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


### EQ-5D average score
```{r}
df_dta %>%
  filter(fCRITERION == "Impact on general health-related quality of life") %>%
  filter(fINDICATOR == "EQ-5D average score") %>%
  distinct(CATEGORIES, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


## Impact on life expectancy
```{r}
df_dta %>%
  filter(fCRITERION == "Impact on life expectancy") %>%
  distinct(fINDICATOR, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


### Years of Life Lost
```{r}
df_dta %>%
  filter(fCRITERION == "Impact on life expectancy") %>%
  filter(fINDICATOR == "Years of Life Lost") %>%
  distinct(CATEGORIES, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


### Years of Life Lost (per death)
```{r}
df_dta %>%
  filter(fCRITERION == "Impact on life expectancy") %>%
  filter(fINDICATOR == "Years of Life Lost (per death)") %>%
  distinct(CATEGORIES, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


## Impact on physical health
```{r}
df_dta %>%
  filter(fCRITERION == "Impact on physical health") %>%
  distinct(fINDICATOR, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


### Experienced burden of physical symptoms
```{r}
df_dta %>%
  filter(fCRITERION == "Impact on physical health") %>%
  filter(fINDICATOR == "Experienced burden of physical symptoms") %>%
  distinct(CATEGORIES, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


### Pain/discomfort
```{r}
df_dta %>%
  filter(fCRITERION == "Impact on physical health") %>%
  filter(fINDICATOR == "Pain/discomfort") %>%
  distinct(CATEGORIES, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


## Impact on psychological health
```{r}
df_dta %>%
  filter(fCRITERION == "Impact on psychological health") %>%
  distinct(fINDICATOR, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


### Anxiety/depression
```{r}
df_dta %>%
  filter(fCRITERION == "Impact on psychological health") %>%
  filter(fINDICATOR == "Anxiety/depression") %>%
  distinct(CATEGORIES, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


### Experienced burden of psychological symptoms related to the health issue
```{r}
df_dta %>%
  filter(fCRITERION == "Impact on psychological health") %>%
  filter(fINDICATOR == "Experienced burden of psychological symptoms related to the health issue") %>%
  distinct(CATEGORIES, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


### Experienced burden of psychological symptoms
```{r}
df_dta %>%
  filter(fCRITERION == "Impact on psychological health") %>%
  filter(fINDICATOR == "Experienced burden of psychological symptoms") %>%
  distinct(CATEGORIES, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


## Accessibility
```{r}
df_dta %>%
  filter(fCRITERION == "Accessibility") %>%
  distinct(fINDICATOR, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


### Foregone care
```{r}
df_dta %>%
  filter(fCRITERION == "Accessibility") %>%
  filter(fINDICATOR == "Foregone care") %>%
  distinct(CATEGORIES, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


### Treatment availability
```{r}
df_dta %>%
  filter(fCRITERION == "Accessibility") %>%
  filter(fINDICATOR == "Treatment availability") %>%
  distinct(CATEGORIES, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


## Burden of treatment
```{r}
df_dta %>%
  filter(fCRITERION == "Burden of treatment") %>%
  distinct(fINDICATOR, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


### Experienced burden of side-effects of treatment
```{r}
df_dta %>%
  filter(fCRITERION == "Burden of treatment") %>%
  filter(fINDICATOR == "Experienced burden of side-effects of treatment") %>%
  distinct(CATEGORIES, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


### Experienced burden of treatment
```{r}
df_dta %>%
  filter(fCRITERION == "Burden of treatment") %>%
  filter(fINDICATOR == "Experienced burden of treatment") %>%
  distinct(CATEGORIES, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


## Effectiveness of treatment
```{r}
df_dta %>%
  filter(fCRITERION == "Effectiveness of treatment") %>%
  distinct(fINDICATOR, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


### Effectiveness of treatment
```{r}
df_dta %>%
  filter(fCRITERION == "Effectiveness of treatment") %>%
  filter(fINDICATOR == "Effectiveness of treatment") %>%
  distinct(CATEGORIES, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


## Quality of care
```{r}
df_dta %>%
  filter(fCRITERION == "Quality of care") %>%
  distinct(fINDICATOR, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


### Clarity of information received
```{r}
df_dta %>%
  filter(fCRITERION == "Quality of care") %>%
  filter(fINDICATOR == "Clarity of information received") %>%
  distinct(CATEGORIES, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


###	Diagnostic timing
```{r}
df_dta %>%
  filter(fCRITERION == "Quality of care") %>%
  filter(fINDICATOR == "Diagnostic timing") %>%
  distinct(CATEGORIES, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


###	Experience with the organisation of care
```{r}
df_dta %>%
  filter(fCRITERION == "Quality of care") %>%
  filter(fINDICATOR == "Experience with the organisation of care") %>%
  distinct(CATEGORIES, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


###	Involvement in treatment choice
```{r}
df_dta %>%
  filter(fCRITERION == "Quality of care") %>%
  filter(fINDICATOR == "Involvement in treatment choice") %>%
  distinct(CATEGORIES, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


###	Quantity of information received
```{r}
df_dta %>%
  filter(fCRITERION == "Quality of care") %>%
  filter(fINDICATOR == "Quantity of information received") %>%
  distinct(CATEGORIES, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


## Financial consequences
```{r}
df_dta %>%
  filter(fCRITERION == "Financial consequences") %>%
  distinct(fINDICATOR, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


### Non-healthcare costs
```{r}
df_dta %>%
  filter(fCRITERION == "Financial consequences") %>%
  filter(fINDICATOR == "Non-healthcare costs") %>%
  distinct(CATEGORIES, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


### Out-of-pocket healthcare costs
```{r}
df_dta %>%
  filter(fCRITERION == "Financial consequences") %>%
  filter(fINDICATOR == "Out-of-pocket healthcare costs") %>%
  distinct(CATEGORIES, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


## Impact of social life
```{r}
df_dta %>%
  filter(fCRITERION == "Impact of social life") %>%
  distinct(fINDICATOR, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


### Social support needs
```{r}
df_dta %>%
  filter(fCRITERION == "Impact of social life") %>%
  filter(fINDICATOR == "Social support needs") %>%
  distinct(CATEGORIES, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


## Impact on work
```{r}
df_dta %>%
  filter(fCRITERION == "Impact on work") %>%
  distinct(fINDICATOR, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


### Changes in working time
```{r}
df_dta %>%
  filter(fCRITERION == "Impact on work") %>%
  filter(fINDICATOR == "Changes in working time") %>%
  distinct(CATEGORIES, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


## Frequency
```{r}
df_dta %>%
  filter(fCRITERION == "Frequency") %>%
  distinct(fINDICATOR, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


### Incidence or prevalence
```{r}
df_dta %>%
  filter(fCRITERION == "Frequency") %>%
  filter(fINDICATOR == "Incidence or prevalence") %>%
  distinct(CATEGORIES, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


### Prevalence
```{r}
df_dta %>%
  filter(fCRITERION == "Frequency") %>%
  filter(fINDICATOR == "Prevalence") %>%
  distinct(CATEGORIES, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


## Preventability
```{r}
df_dta %>%
  filter(fCRITERION == "Preventability") %>%
  distinct(fINDICATOR, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


### Implementation of effective primary prevention strategies
```{r}
df_dta %>%
  filter(fCRITERION == "Preventability") %>%
  filter(fINDICATOR == "Implementation of effective primary prevention strategies") %>%
  distinct(CATEGORIES, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


## Productivity losses
```{r}
df_dta %>%
  filter(fCRITERION == "Productivity losses") %>%
  distinct(fINDICATOR, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


### Costs related to work absenteeism, presenteeism or/and early labor force exits of caregivers
```{r}
df_dta %>%
  filter(fCRITERION == "Productivity losses") %>%
  filter(fINDICATOR == "Costs related to work absenteeism, presenteeism or/and early labor force exits of caregivers") %>%
  distinct(CATEGORIES, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


### Costs related to work absenteeism, presenteeism, early labor force exits of patients
```{r}
df_dta %>%
  filter(fCRITERION == "Productivity losses") %>%
  filter(fINDICATOR == "Costs related to work absenteeism, presenteeism, early labor force exits of patients") %>%
  distinct(CATEGORIES, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


## Forecasted healthcare costs
```{r}
df_dta %>%
  filter(fCRITERION == "Forecasted healthcare costs") %>%
  distinct(fINDICATOR, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


### Forecasted healthcare costs attributable to the health condition
```{r}
df_dta %>%
  filter(fCRITERION == "Forecasted healthcare costs") %>%
  filter(fINDICATOR == "Forecasted healthcare costs attributable to the health condition") %>%
  distinct(CATEGORIES, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


## Forecasted productivity losses
```{r}
df_dta %>%
  filter(fCRITERION == "Forecasted productivity losses") %>%
  distinct(fINDICATOR, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


### Forecasted productivity losses attributable to the health condition
```{r}
df_dta %>%
  filter(fCRITERION == "Forecasted productivity losses") %>%
  filter(fINDICATOR == "Forecasted productivity losses attributable to the health condition") %>%
  distinct(CATEGORIES, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


## Impact on social life
```{r}
df_dta %>%
  filter(fCRITERION == "Impact on social life") %>%
  distinct(fINDICATOR, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


### Social support needs
```{r}
df_dta %>%
  filter(fCRITERION == "Impact on social life") %>%
  filter(fINDICATOR == "Social support needs") %>%
  distinct(CATEGORIES, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


## Burden on informal caregivers
```{r}
df_dta %>%
  filter(fCRITERION == "Burden on informal caregivers") %>%
  distinct(fINDICATOR, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


### Loss in informal caregiver’s quality of life	
```{r}
df_dta %>%
  filter(fCRITERION == "Burden on informal caregivers") %>%
  filter(fINDICATOR == "Loss in informal caregiver’s quality of life") %>%
  distinct(CATEGORIES, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


## Value for money of standard of care
```{r}
df_dta %>%
  filter(fCRITERION == "Value for money of standard of care") %>%
  distinct(fINDICATOR, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


### Healthcare costs per unit of health gain	
```{r}
df_dta %>%
  filter(fCRITERION == "Value for money of standard of care") %>%
  filter(fINDICATOR == "Healthcare costs per unit of health gain") %>%
  distinct(CATEGORIES, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


## Environmental impact of standard of care 
```{r}
df_dta %>%
  filter(fCRITERION == "Environmental impact of standard of care") %>%
  distinct(fINDICATOR, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```


### Hazardous waste related to standard of care
```{r}
df_dta %>%
  filter(fCRITERION == "Environmental impact of standard of care") %>%
  filter(fINDICATOR == "Hazardous waste related to standard of care") %>%
  distinct(CATEGORIES, fDISEASE) %>%
  mutate(value = "✓") %>%
  pivot_wider(names_from = fDISEASE,
              values_from = value,
              values_fill = "") %>%
  kable()
```






