
### Rows without (VALUE & KEYPOINT & QUOTE)

Now the rows that cannot be used for our purpose will be deleted from the dataset. These are all rows that don't have a value, keypoint and quote.
Except the ones where there is a useful comment or meta that can be used, or the ones where a criterion does not need a value.
This needs to be evaluated manually for every row.

```{r}
df_dta_nodata <- df_dta[is.na(df_dta$VALUE) & is.na(df_dta$KEY_POINT) & is.na(df_dta$QUOTES), 
             c("fCRITERION", "fINDICATOR", "MEASURE", "UNIT", "CATEGORIES", "META_1", "META_2", "COMMENTS")]

dim(df_dta)
dim(df_dta_nodata)
kable(df_dta_nodata)
```

*'% of participants who did not return to work (38%) or reduced their working hours (26%) at the time of the survey due to their health status'*
This can be used to obtain two more categories with values, the other rows do not give us any information, so they can be removed.

```{r}
df_dta

# create new rows
old_row <- df_dta[grepl("% of participants who did not return to work", df_dta$META_1), ]
old_row

new_row_1 <- old_row
new_row_1$CATEGORIES <- '% of participants who did not return to work at the time of the survey due to their health status'
new_row_1$VALUE <- '38'
new_row_1$VALUE_num <- 38
new_row_1

new_row_2 <- old_row
new_row_2$CATEGORIES <- '% of participants who reduced their working hours at the time of the survey due to their health status'
new_row_2$VALUE <- '26'
new_row_2$VALUE_num <- 26

df_dta_new <- rbind(df_dta[df_dta$META_1 != old_row$META_1, ], new_row_1, new_row_2)
df_dta_new

# remove old rows

```


### Rows without category

In the data there is still one potential issue. There could be rows without a category, that still have a value, keypoint or quote. 
These need to be examined carefully as the category often can be extracted from the context of the values and measure or if the indicator serves as the category.

```{r}
df_filtered <- df_dta %>%
  filter(is.na(CATEGORIES)) %>%
  mutate(
    Has_KEY_POINT = ifelse(!is.na(KEY_POINT), "Yes", "No"),
    Has_QUOTE = ifelse(!is.na(QUOTES), "Yes", "No")
  ) %>%
  select(fID, fCRITERION, fINDICATOR, MEASURE, UNIT, VALUE, Has_KEY_POINT, Has_QUOTE)

kable(df_filtered, caption = "Rows with NA in CATEGORIES")
```

The empty categories are the result of an indicator having only one row, then, different categories are not necessary.
We can look where this is the case and take another look at the data with this new information.

```{r}
df_filtered <- df_dta %>%
  filter(is.na(CATEGORIES)) %>%
  mutate(
    Has_KEY_POINT = ifelse(!is.na(KEY_POINT), "Yes", "No"),
    Has_QUOTE = ifelse(!is.na(QUOTES), "Yes", "No")
  ) %>%
  group_by(fID, fINDICATOR) %>% 
  filter(n() >= 2) %>%
  ungroup() %>%
  select(fID, fCRITERION, fINDICATOR, MEASURE, UNIT, VALUE, Has_KEY_POINT, Has_QUOTE)

kable(df_filtered, caption = "Duplicate (fID & fINDICATOR) Rows with NA in CATEGORIES")

dim(df_dta)
```

There seems to be a mix up here between **VALUE** and **CATEGORIES**. 
The rows look like they mean that if the treatment is very effective, than you have these quotes and keypoints.
And, when the treatment is moderately effective, there is also a keypoint.
Both keypoints are the exact same, but this does not necessarily mean we can remove the data.
We can however change the value to a category.

```{r}
# change VALUE and CATEGORY
df_dta <- df_dta %>%
  mutate(
    CATEGORIES = ifelse(fID == "Malignant melanoma" & 
                        fINDICATOR == "Effectiveness of treatment" & 
                        VALUE == "Very effective", VALUE, CATEGORIES),
    
    VALUE = ifelse(fID == "Malignant melanoma" & 
                   fINDICATOR == "Effectiveness of treatment" & 
                   VALUE == "Very effective", "0", VALUE)
  )


df_dta <- df_dta %>%
  mutate(
    CATEGORIES = ifelse(fID == "Malignant melanoma" & 
                        fINDICATOR == "Effectiveness of treatment" & 
                        VALUE == "Very effective", VALUE, CATEGORIES),
    
    VALUE = ifelse(fID == "Malignant melanoma" & 
                   fINDICATOR == "Effectiveness of treatment" & 
                   VALUE == "Moderately effective", "0", VALUE)
  )


```



### cleaned dataset
```{r}
dim(df_dta)

head(df_dta)
```






























