
### Rows without (VALUE & KEYPOINT & QUOTE)

Now the rows that cannot be used for our purpose will be deleted from the dataset. These are all rows that don't have a value, keypoint and quote.
Except the ones where there is a useful comment or meta that can be used, or the ones where a criterion does not need a value.
This needs to be evaluated manually for every row.

```{r}
df_dta_nodata <- df_dta[is.na(df_dta$VALUE) & is.na(df_dta$KEY_POINT) & is.na(df_dta$QUOTES), 
             c("fCRITERION", "fINDICATOR", "CATEGORIES", "MEASURE", "UNIT", "CATEGORIES", "META_1", "META_2", "COMMENTS")]

dim(df_dta)
dim(df_dta_nodata)
kable(df_dta_nodata)
```

*'% of participants who did not return to work (38%) or reduced their working hours (26%) at the time of the survey due to their health status'*
This can be used to obtain two more categories with values, the other rows do not give us any information, so they can be removed.

```{r}
# create new rows
old_row <- df_dta[grepl("% of participants who did not return to work", df_dta$META_1), ]
old_row

new_row_1 <- old_row
new_row_1$CATEGORIES <- '% of participants who did not return to work at the time of the survey due to their health status'
new_row_1$VALUE <- '38'
new_row_1$VALUE_num <- 38

new_row_2 <- old_row
new_row_2$CATEGORIES <- '% of participants who reduced their working hours at the time of the survey due to their health status'
new_row_2$VALUE <- '26'
new_row_2$VALUE_num <- 26

df_dta <- rbind(df_dta, new_row_1, new_row_2)
```
```{r}
# remove old rows
df_dta <- df_dta[!is.na(df_dta$VALUE) | !is.na(df_dta$KEY_POINT) | !is.na(df_dta$QUOTES), ]
head(df_dta)
dim(df_dta)
```



### Rows without category

In the data there is still one potential issue. There could be rows without a category, that still have a value, keypoint or quote. 
These need to be examined carefully as the category often can be extracted from the context of the values and measure or if the indicator serves as the category.

```{r}
df_filtered <- df_dta %>%
  filter(is.na(CATEGORIES)) %>%
  mutate(
    Has_KEY_POINT = ifelse(!is.na(KEY_POINT), "Yes", "No"),
    Has_QUOTE = ifelse(!is.na(QUOTES), "Yes", "No")
  ) %>%
  select(fDISEASE, fCRITERION, fINDICATOR, MEASURE, UNIT, VALUE, Has_KEY_POINT, Has_QUOTE)

kable(df_filtered, caption = "Rows with NA in CATEGORIES")
```

The empty categories are the result of an indicator having only one row, so different categories are not necessary.
We can look where this is the case and take another look at the data with this new information.

```{r}
df_filtered <- df_dta %>%
  filter(is.na(CATEGORIES)) %>%
  mutate(
    Has_KEY_POINT = ifelse(!is.na(KEY_POINT), "Yes", "No"),
    Has_QUOTE = ifelse(!is.na(QUOTES), "Yes", "No")
  ) %>%
  group_by(fDISEASE, fINDICATOR) %>% 
  filter(n() >= 2) %>%
  ungroup() %>%
  select(fDISEASE, fCRITERION, fINDICATOR, MEASURE, UNIT, VALUE, Has_KEY_POINT, Has_QUOTE)

kable(df_filtered, caption = "Duplicate (fDISEASE & fINDICATOR) Rows with NA in CATEGORIES")

dim(df_dta)
```


### Character values

The character values are hard to use in any kind of model here. We won't remove them, but we probably won't be able to use them. The 'Not applicable'-value however can be removed, because it has not other value, keypoint and quote, and evidently is not applicable
```{r}
kable(
  df_dta[!is.na(df_dta$VALUE_char), c("fDISEASE", "fCRITERION", "fINDICATOR", "CATEGORIES", "VALUE_char")],
  caption = "Filtered Data Table",
  format = "markdown"
)
```

```{r}
df_dta <- df_dta[is.na(df_dta$VALUE_char) | df_dta$VALUE_char != "Not applicable", ]
```



### Removing empty rows

fINDICATOR_PROXY can be removed as it has only NA-values.
```{r}
df_dta$fINDICATOR_PROXY <- NULL
```


### cleaned dataset
```{r}
# sort data
df_dta <- df_dta %>%
  arrange(fDISEASE, fDIMENSION, fDOMAIN, fCRITERION, fINDICATOR, CATEGORIES)
```

```{r}
dim(df_dta)

head(df_dta)
```






























