
A lot of analysis between certain variables is not useful, or at least not to great extend, so they are not done here.
**SEX** will be analysed first, because there is something going on with it that will give a skewed view of the other variables.

### Sex
#### Disease x Sex
```{r}
crossTable <- table(df_dta$fDISEASE, df_dta$fSEX)
crossTable_df <- as.data.frame.matrix(crossTable)
kable(crossTable_df, caption = "Cross Table of fDISEASE and fDISEASE_SUBTYPE")
```
The data shows for every disease the data for both sexes, and than for each sex separately.
These numbers do not add up under this assumption, however.
This will be explored under the **SEX**-subsection.


#### Disease x Sex x Criterion
```{r}
df_dta_temp <- df_dta[df_dta$fDISEASE == "Crohns Disease", ]
crossTable <- table(df_dta_temp$fCRITERION, df_dta_temp$fSEX)
crossTable_df <- as.data.frame.matrix(crossTable)
kable(crossTable_df, caption = "Crohns Disease: Cross Table of fCRITERION and fSEX")

df_dta_temp <- df_dta[df_dta$fDISEASE == "Long COVID", ]
crossTable <- table(df_dta_temp$fCRITERION, df_dta_temp$fSEX)
crossTable_df <- as.data.frame.matrix(crossTable)
kable(crossTable_df, caption = "Long COVID: Cross Table of fCRITERION and fSEX")

df_dta_temp <- df_dta[df_dta$fDISEASE == "Malignant melanoma", ]
crossTable <- table(df_dta_temp$fCRITERION, df_dta_temp$fSEX)
crossTable_df <- as.data.frame.matrix(crossTable)
kable(crossTable_df, caption = "Malignant melanoma: Cross Table of fCRITERION and fSEX")
```

One example is printed out to see the problem with the missing criteria.
```{r}
df_dta[df_dta$fDISEASE == "Crohns Disease" & df_dta$fCRITERION == "Burden of treatment", ]
```
The missing data with the specific sexes seems to just be that the categories are not filled in. 
Therefore, there is no reason to show an indicator multiple times.


#### Disease x Sex x (Value, Keypoint, Quote)
```{r}
df_dta %>%
  filter(fDISEASE == "Crohns Disease") %>%
  group_by(fSEX) %>%  # Group by sex
  summarise(
    proportion_non_missing = mean(!is.na(VALUE) | !is.na(KEY_POINT) | !is.na(QUOTES))  # Check if any column is non-missing
  ) %>%
  kable(digits = 3, col.names = c("Sex", "Chrohns Disease: Proportion (Value or Keypoint or Quote not missing)"))

df_dta %>%
  filter(fDISEASE == "Long COVID") %>%
  group_by(fSEX) %>%  # Group by sex
  summarise(
    proportion_non_missing = mean(!is.na(VALUE) | !is.na(KEY_POINT) | !is.na(QUOTES))  # Check if any column is non-missing
  ) %>%
  kable(digits = 3, col.names = c("Sex", "Long COVID: Proportion (Value or Keypoint or Quote not missing)"))

df_dta %>%
  filter(fDISEASE == "Malignant melanoma") %>%
  group_by(fSEX) %>%  # Group by sex
  summarise(
    proportion_non_missing = mean(!is.na(VALUE) | !is.na(KEY_POINT) | !is.na(QUOTES))  # Check if any column is non-missing
  ) %>%
  kable(digits = 3, col.names = c("Sex", "Malignant melanoma: Proportion (Value or Keypoint or Quote not missing)"))
```
Most of the data under the specific sexes are missing. 
Seeing as this data is a subdivision of the 'both sexes'-category we can just use this one category.
We just will not be able to make predictions or decisions based on the specific sex.

Just to be sure the non-missing data is prined out.
```{r}
df_dta[(!is.na(df_dta$VALUE) | !is.na(df_dta$KEY_POINT) | !is.na(df_dta$QUOTES)) & (df_dta$fSEX == "Men" | df_dta$fSEX == "Women"), ]
```

This is not enough data to work with, the specific sexes rows will be removed.
```{r}
df_dta <- df_dta[df_dta$fSEX == "Both sexes", ]
df_dta$fSEX <- NULL
dim(df_dta)
```



### Disease
#### Disease x Dimension
```{r}
crossTable <- table(df_dta$fDISEASE, df_dta$fDIMENSION)
crossTable_df <- as.data.frame.matrix(crossTable)
kable(crossTable_df, caption = "Cross Table of fDISEASE and fDIMENSION")
```
All dimensions are accounted for, for all diseases, and can be used to differentiate between different dimensions of the indicators.


#### Disease x Domain
```{r}
crossTable <- table(df_dta$fDISEASE, df_dta$fDOMAIN)
crossTable_df <- as.data.frame.matrix(crossTable)
kable(crossTable_df, caption = "Cross Table of fDISEASE and fDOMAIN")
```
The same comments apply to domain as to dimension.


#### Disease x Criterion
```{r}
crossTable <- table(df_dta$fCRITERION, df_dta$fDISEASE)
crossTable_df <- as.data.frame.matrix(crossTable)
kable(crossTable_df, caption = "Cross Table of fCRITERION and fID")
```
All diseases seem to cover all criteria, this makes it possible for us to determine urgency levels separately for the diseases.
However, not all diseases cover the same indicators per criterion as we will see later.


#### Missing values per disease
```{r}
# Define variables of interest
vars <- c("MEASURE", "UNIT", "CATEGORIES", "VALUE_num", "VALUE_char", "KEY_POINT", "QUOTES", "META_1", "META_2", "COMMENTS")

# Calculate proportion of missing values per disease
missing_table <- sapply(vars, function(var) {
  tapply(is.na(df_dta[[var]]), df_dta$fDISEASE, mean, na.rm = TRUE)
})

# Convert to a data frame
missing_table_df <- as.data.frame(t(missing_table))

# Print as a formatted table
kable(digits=2, missing_table_df, caption = "Proportion of Missing Values per Disease")
```
There are a big amount of missing rows for these variables. The meta and comments-data even has barely any filled-in columns.
In the data cleaning we will have to carefully traverse these rows to see which ones are usable.


#### Comments
It is not useful to analyse any of the other variables together (bivariatly) with **fDISEASE**, because the other variables are all in function of the indicators.
Indicators x Disease is only relevant itself in reference to the criteria. 
Columns like: **MEASURE**, **UNIT**, **CATEGORIES** are here analyzed together with the diseases, but only to see the distribution of missing values.
Comparing all their actual values to **fDISEASE** does not make sense bivariatly.


### Criterion & indicator
#### Disease x Criterion x Indicator
```{r}
# Crohns disease
grouped_df <- df_dta[df_dta$fDISEASE == "Crohns Disease", ] %>%
  filter(!is.na(fCRITERION), !is.na(fINDICATOR)) %>%
  group_by(fCRITERION) %>%
  summarise(Indicators = paste(unique(fINDICATOR), collapse = " | ")) %>%
  ungroup()

kable(grouped_df, caption = "Crohns Disease: fCRITERION and Associated fINDICATORs")


# long covid
grouped_df <- df_dta[df_dta$fDISEASE == "Long COVID", ] %>%
  filter(!is.na(fCRITERION), !is.na(fINDICATOR)) %>%
  group_by(fCRITERION) %>%
  summarise(Indicators = paste(unique(fINDICATOR), collapse = " | ")) %>%
  ungroup()

kable(grouped_df, caption = "Long COVID: fCRITERION and Associated fINDICATORs")


# malgnant melanoma
grouped_df <- df_dta[df_dta$fDISEASE == "Malignant melanoma", ] %>%
  filter(!is.na(fCRITERION), !is.na(fINDICATOR)) %>%
  group_by(fCRITERION) %>%
  summarise(Indicators = paste(unique(fINDICATOR), collapse = " | ")) %>%
  ungroup()

kable(grouped_df, caption = "Malignant melanoma: fCRITERION and Associated fINDICATORs")
```
All diseases contain all indicators for the same criteria, although some may not have enough data.


#### Comments
evaluating criterion (or Indicator) with the other variables will not give us any new useful information.
What we could gain from this is seeing how much data misses per criterion (or indicator), but unusable missing data will be cleaned and analysed anyway in the data cleaning step.

### Measure & Unit
#### Measure x Unit x value
```{r}
crosstable <- df_dta %>%
  mutate(
    MEASURE_present = !is.na(MEASURE),
    VALUE_present   = !is.na(VALUE),
    UNIT_present    = !is.na(UNIT)
  ) %>%
  count(MEASURE_present, VALUE_present, UNIT_present) %>%
  arrange(desc(n))

print(crosstable)
```
There are no rows where the measure has a value, but the unit does not. So for every measure we have a unit.
Vice versa, this is not the case. In the data cleaning we will need to go row by row and analyse if there are among these any unusable rows.
There are a few measures and units that have no value, they may still have keypoints and/or quotes.
There are also values without a measure or unit. In this case the meaning of these values might be deduced from the indicators or categories.


### Value & keypoints & quotes
#### Value x Keypoint x Quotes
```{r}
crosstable <- df_dta %>%
  mutate(
    MEASURE_present = !is.na(VALUE),
    VALUE_present   = !is.na(KEY_POINT),
    UNIT_present    = !is.na(QUOTES)
  ) %>%
  count(MEASURE_present, VALUE_present, UNIT_present) %>%
  arrange(desc(n))

print(crosstable)
```
There are 67 rows where there are no values, keypoints and quotes. In theory these rows can than not be used. There are, however, some possible exceptions as mentioned before.


### SD x CI
```{r}
filtered_df <- df_dta[!is.na(df_dta$SD) | !is.na(df_dta$`LOWER CI`) | !is.na(df_dta$`UPPER CI`), 
                      c('VALUE_num', 'SD', 'LOWER CI', 'UPPER CI')]

# Create kable table
kable(filtered_df, caption = "Summary of SD and Confidence Intervals", digits = 3)

summary(filtered_df)
```


### Conclusion
There are a lot of possibilities where the rows can become unusable, in the data cleaning step we will need to carefully filter or alter the rows to be able to use them.

In theory if in a row none of the following variables is present, the row is unusable:
* VALUE
* KEY_POINT
* QUOTES
If any of these is present the row should give information, but with the amount of missing categories, units and measures it is possible that we cannot get information out of the row.

Rows without these variables may still become useful if there is more information in one of the following:
* INDICATOR
* CATEGORIES
* META/COMMENTS
























