
### ID
```{r}
# convert to factor
typeof(df_dta$ID)
df_dta$fDISEASE <- as.factor(df_dta$ID)
df_dta <- df_dta %>% relocate(fDISEASE, .after = ID)
df_dta$ID <- NULL

# levels
table(df_dta$fDISEASE)

# na values
sum(is.na(df_dta$fDISEASE))
```
This variable partitions all data points into the disease they belong to:

* **Chrons Disease:** A type of inflammatory bowel disease (IBD) that causes chronic inflammation of the digestive tract.
* **Long COVID:** (also called post-COVID syndrome) Refers to ongoing symptoms that persist for weeks or months after recovering from a COVID-19 infection.
* **Malignant melanoma:** The most serious type of skin cancer that develops in the melanocytes, the cells that produce melanin (the pigment that gives skin its color).

All rows have an id, so no cleaning needs to be done yet on the basis of this variable.
The choice to rename this variable to fDISEASE instead of fID stems from the analysis of the DISEASE variable further.
This name more accurately represents what the variable is about.


### Sex
```{r}
# convert to factor
typeof(df_dta$SEX)
df_dta$fSEX <- as.factor(df_dta$SEX)
df_dta <- df_dta %>% relocate(fSEX, .after = SEX)
df_dta$SEX <- NULL

# levels
table(df_dta$fSEX)

# na values
sum(is.na(df_dta$fSEX))
```
This variable divides the data into the sexes. 
It has for every criteria/category a value for both sexes and for every sex separately.
This can be useful to compare what unmet needs are more urgent for each sex. 


### AGE
```{r}
# levels
table(df_dta$AGE)

# na values
sum(is.na(df_dta$AGE))

# remove column
df_dta$AGE <- NULL
```
All values are the same for this variable and are not informative.
Therefore this column can be safely removed.


### SES
```{r}
# levels
table(df_dta$SES)

# na values
sum(is.na(df_dta$SES))

# remove column
df_dta$SES <- NULL
```
This has the same issue as **AGE**, thus can be removed.


### Dimension
```{r}
# convert to factor
typeof(df_dta$DIMENSION)
df_dta$fDIMENSION <- as.factor(df_dta$DIMENSION)
df_dta <- df_dta %>% relocate(fDIMENSION, .after = DIMENSION)
df_dta$DIMENSION <- NULL

# levels
table(df_dta$fDIMENSION)

# na values
sum(is.na(df_dta$fDIMENSION))
```
The dimension of the criteria, meaning what part it applies to.


### Domain
```{r}
# convert to factor
typeof(df_dta$DOMAIN)
df_dta$fDOMAIN <- as.factor(df_dta$DOMAIN)
df_dta <- df_dta %>% relocate(fDOMAIN, .after = DOMAIN)
df_dta$DOMAIN <- NULL

# levels
table(df_dta$fDOMAIN)

# na values
sum(is.na(df_dta$fDOMAIN))
```
This variable serves a similar purpose as **DIMENSION**. It separates the criteria in various categories to which they apply.


### Criterion
```{r}
# convert to factor
df_dta$fCRITERION <- as.factor(df_dta$CRITERION)
df_dta <- df_dta %>% relocate(fCRITERION, .after = CRITERION)
df_dta$CRITERION <- NULL

# levels
criterion_table <- as.data.frame(table(df_dta$fCRITERION))
kable(criterion_table, format = "markdown")

# na values
sum(is.na(df_dta$fCRITERION))
```
These are the criteria we need to label in this thesis.


### Indicator
```{r}
# convert to factor
df_dta$fINDICATOR <- as.factor(df_dta$INDICATOR)
df_dta <- df_dta %>% relocate(fINDICATOR, .after = INDICATOR)
df_dta$INDICATOR <- NULL

# levels
indicator_table <- as.data.frame(table(df_dta$fINDICATOR))
kable(indicator_table, format = "markdown")

# na values
sum(is.na(df_dta$fINDICATOR))
```
All rows have an indicator. 
This variable gives for each criterion certain indicators and is just like criterion an essential variable for each row.


### Disease
```{r}
# convert to factor
typeof(df_dta$DISEASE)

# levels
table(df_dta$DISEASE)
df_dta$fDISEASE[as.character(df_dta$fDISEASE) != df_dta$DISEASE]
df_dta$DISEASE[as.character(df_dta$fDISEASE) != df_dta$DISEASE]

# remove column
df_dta$DISEASE <- NULL
```
This is the exact same variable as ID, so the column can be removed.


### Disease subtype
```{r}
# convert to factor
typeof(df_dta$DISEASE_SUBTYPE)
df_dta$fDISEASE_SUBTYPE <- as.factor(df_dta$DISEASE_SUBTYPE)
df_dta <- df_dta %>% relocate(fDISEASE_SUBTYPE, .after = DISEASE_SUBTYPE)
df_dta$DISEASE_SUBTYPE <- NULL

# levels
table(df_dta$fDISEASE_SUBTYPE)

# na values
sum(is.na(df_dta$fDISEASE_SUBTYPE))
```
This variable reports on different subtypes within a disease. 
It seems little reported on, so this is probably not useful for the priority system.


### Disease proxy
```{r}
# convert to factor
typeof(df_dta$DISEASE_PROXY)
df_dta$fDISEASE_PROXY <- as.factor(df_dta$DISEASE_PROXY)
df_dta <- df_dta %>% relocate(fDISEASE_PROXY, .after = DISEASE_PROXY)
df_dta$DISEASE_PROXY <- NULL

# levels
table(df_dta$fDISEASE_PROXY)

# na values
sum(is.na(df_dta$fDISEASE_PROXY))
```
This variable does not seem useful, as Crohn's disease is a subtype of IBD.
Malgnant melanoma is a type of skin cancer, therefore *Malignant melanoma*, *Malignant melanoma of skin* and *skin cancer* are all the same thing under the disease *Malignant melanoma*.


### Country
```{r}
# levels
table(df_dta$COUNTRY)

# na values
sum(is.na(df_dta$COUNTRY))

# remove column
df_dta$COUNTRY <- NULL
```
In each row the value is the same, except for missing values.
We will remove the column here and just mention in the data-section of the thesis that the data is all either obtained from Belgium or unknown.
Note that this unknown data is most likely also from Belgium as that is where the data gathering took place, and all rows in the previous dataset where from Belgium.


### Country proxy
```{r}
# convert to factor
typeof(df_dta$COUNTRY_PROXY)
df_dta$fCOUNTRY_PROXY <- as.factor(df_dta$COUNTRY_PROXY)
df_dta <- df_dta %>% relocate(fCOUNTRY_PROXY, .after = COUNTRY_PROXY)
df_dta$COUNTRY_PROXY <- NULL

# levels
table(df_dta$fCOUNTRY_PROXY)

# na values
sum(is.na(df_dta$fCOUNTRY_PROXY))
```
This variable has only a few variables, but will be left in the dataset because it does show distinction between datapoints
The 'na'-values may just be an indicator that the data is obtained from Belgium.


### Year
```{r}
# levels
table(df_dta$YEAR)

# na values
sum(is.na(df_dta$YEAR))

# histogram
hist(df_dta$YEAR)

# explain outliers
df_dta[df_dta$YEAR == 2014 & !is.na(df_dta$YEAR), "SOURCE"]
df_dta[df_dta$SOURCE == "Pil et al. 2016" & !is.na(df_dta$SOURCE), "YEAR"]

# correct column
df_dta$YEAR[df_dta$YEAR == 2034] = 2014
table(df_dta$YEAR)
```
The four datapoints from 2014 are weird, but not impossible, and not improbable enough to remove.
Two rows have the year 2034. at first we thought this was a typo for 2024.
Upon further analysis we see that all the datapoints with year 2014 are sourced from a study of 2016, this makes sense with the data.
However the 2034 columns also come from this study, leading us to the conclusion that they should be from 2014.


### Indicator proxy
```{r}
# convert to factor
typeof(df_dta$INDICATOR_PROXY)
df_dta$fINDICATOR_PROXY <- as.factor(df_dta$INDICATOR_PROXY)
df_dta <- df_dta %>% relocate(fINDICATOR_PROXY, .after = INDICATOR_PROXY)
df_dta$INDICATOR_PROXY <- NULL

# levels
table(df_dta$fINDICATOR_PROXY)

# na values
sum(is.na(df_dta$fINDICATOR_PROXY))
```
This does not tell us a lot, the variable will be left in the table, but won't be used.


### Measure
```{r}
# levels
table <- as.data.frame(table(df_dta$MEASURE))
kable(table, format = "markdown")

# na values
sum(is.na(df_dta$MEASURE))
```
These are the measures by which a category is portrayed. 
A lot of the rows do not have measures, but these may still be useful since it might be deduced from the indicator, comment or meta.


### Unit
```{r}
# levels
table <- as.data.frame(table(df_dta$UNIT))
kable(table, format = "markdown")

# na values
sum(is.na(df_dta$UNIT))
```
These are the units for each measure. There is a lot of missing data, but the measure mostly tells us already what this should be.
To normalize the values it will be important to correctly interpret the missing data however.


### Categories
```{r}
# levels
table <- as.data.frame(table(df_dta$CATEGORIES))
kable(table, format = "markdown")

# na values
sum(is.na(df_dta$CATEGORIES))
```
For each indicator there are various categories. The value for each category is regulated by a measure and unit for the measure.
It seems to differ a lot between categories, which is a problem for clustering. We might need to find another way to classify their importance, perhaps in a more semi-supervised way. For this we would need to gather more data ourselves from experts.


### Value 
```{r}
# na values
sum(is.na(df_dta$VALUE))

# value is a character var
typeof(df_dta$VALUE)
df_dta$VALUE[!(df_dta$VALUE=="(Missing)") & is.na(suppressWarnings(as.numeric(df_dta$VALUE)))]

# transform VALUE
df_dta <- df_dta %>%
  mutate(VALUE = na_if(VALUE, "(Missing)"))

# convert to numeric and add extra column for non numeric to not lose data
df_dta$VALUE_num <- suppressWarnings(as.numeric(df_dta$VALUE))
df_dta$VALUE_char <- ifelse(is.na(df_dta$VALUE_num), df_dta$VALUE, NA)
df_dta <- df_dta %>% relocate(VALUE_num, .after = VALUE)
df_dta <- df_dta %>% relocate(VALUE_char, .after = VALUE_num)



df_dta[, c("VALUE_num", "VALUE_char")]

# analysis
hist(df_dta$VALUE_num, breaks = 10)
```
There are both numerical and plain text values, we separate them so we can work with both.
In the histogram it is apparent that these values are not on the same scale, they should be scaled so different values can be compared.


### SD
```{r}
hist(df_dta$SD, breaks = 10)

# na values
sum(is.na(df_dta$SD))
```
This variable is not often reported upon and can probably not be used for our purposes either.


### Lower CI
```{r}
hist(df_dta$`LOWER CI`, breaks = 10)

# na values
sum(is.na(df_dta$`LOWER CI`))
```


### Upper CI
```{r}
hist(df_dta$`UPPER CI`, breaks = 10)

# na values
sum(is.na(df_dta$`UPPER CI`))
```
These two variables follow the same analysis as **SD**.

### Source
```{r}
table(df_dta$SOURCE)

# na values
sum(is.na(df_dta$SOURCE))
```
This contains the source for the datapoints. 
It is not useful for building the priority model, but it is useful to see where the data came from.

### Rating
```{r}
# non na values
sum(!is.na(df_dta$RATING))

# na values
sum(is.na(df_dta$RATING))

# no values so column can be removed
df_dta$RATING <- NULL
```
This variable contains no data, so it can be safely removed.

### Key points
```{r}
head(df_dta[!is.na(df_dta$KEY_POINT), "KEY_POINT"])

# na values
sum(is.na(df_dta$KEY_POINT))
```
A lot of missing values so we need to have a system where rows without keypoints do not necessarily get a lower score.
This variable needs to stay in plain text for classifying it with NLP.
There are sometimes multiple quotes separated by a ';', we will leave it like this for now.


### Quotes
```{r}
head(df_dta[!is.na(df_dta$QUOTES), "QUOTES"])

# na values
sum(is.na(df_dta$QUOTES))
```
The same applies to the quotes as for the keypoints.


### Meta 1
```{r}
head(df_dta[!is.na(df_dta$META_1), "META_1"])

# na values
sum(is.na(df_dta$META_1))
```
This is extra information about datapoints that needs to be taken into account if we want to remove or alter them.


### Meta 2
```{r}
head(df_dta[!is.na(df_dta$META_2), "META_2"])

# na values
sum(is.na(df_dta$META_2))
```
The same as metadata 1.


### Meta 3
```{r}
head(df_dta[!is.na(df_dta$META_3), "META_3"])

# na values
sum(is.na(df_dta$META_3))

# remove column
df_dta$META_3 <- NULL
```
This column contains no data so it can be removed.


### Criterion 2
```{r}
head(df_dta[!is.na(df_dta$CRITERION2), "CRITERION2"])

# na values
sum(is.na(df_dta$CRITERION2))

# check similarity to criterion 1
df_dta[!is.na(df_dta$CRITERION2) & 
       as.character(df_dta$fCRITERION) != as.character(df_dta$CRITERION2), 
       c("fCRITERION", "CRITERION2")]

# remove column
df_dta$CRITERION2 <- NULL
```
This column seems to contain the exact same data as **CRITERION** except less rows are filled in and it is formulated differently.
This variable can thus be removed.


### Comments
```{r}
head(df_dta[!is.na(df_dta$COMMENTS), "COMMENTS"])

# na values
sum(is.na(df_dta$COMMENTS))
```
Like metadata, some extra information that might be useful.


### Qualy
```{r}
head(df_dta[!is.na(df_dta$QUALY), "QUALY"])

# na values
sum(is.na(df_dta$QUALY))

# no data so remove column
df_dta$QUALY <- NULL
```
This column contains no data, so can be removed.


### Value_Viz
```{r}
print(typeof(df_dta$VALUE_VIZ))

# check difference with VALUE
identical(df_dta$VALUE_num, df_dta$VALUE_VIZ)

# remove column
df_dta$VALUE_VIZ <- NULL
```
This variable is the exact same as the numerical part of **VALUE**. It can therefore be deleted.


## Univariate conclusion
After the univariate analysis the data looks as follows:
```{r}
head(df_dta)
dim(df_dta)
```
The useful variables for further analysis are:

* fDISEASE
* fDIMENSION
* fDOMAIN
* fCRITERION
* fINDICATOR
* YEAR
* MEASURE
* UNIT
* CATEGORIES
* VALUE_num
* VALUE_char
* KEY_POINT
* QUOTES
* META/COMMENTS

The deleted variables are:

* DISEASE
* COUNTRY
* AGE
* SES
* META_3
* RATING
* CRITERION2
* VALUE_VIZ

Either because they were duplicates of other columns or if they contained no values, or all the same ones.

The remaining columns with (substantial) missing data are:
* (fDISEASE_SUBTYPE)
* (fDISEASE_PROXY)
* (fCOUNTRY_PROXY)
* YEAR
* (fINDICATOR_PROXY)
* MEASURE
* UNIT
* CATEGORIES
* VALUE
* SOURCE
* KEY_POINT
* QUOTES
* META/COMMENTS

The variables in brackets are not important for further analysis, since they are too sparse and/or don't tell anything about the diseases or criteria.
They will be left in the dataset to see if we can get any conclusions on these with our model.
For creating the model, they are not useful.

The most important findings are that many of the variables are only sparsely filled in, and we identified the important variables for further analysis.

































