
### ID
```{r}
# convert to factor
typeof(df_dta$ID)
df_dta$fID <- as.factor(df_dta$ID)

# levels
table(df_dta$fID)

# na values
sum(is.na(df_dta$fID))
```

### Disease
```{r}
table(df_dta$DISEASE)
df_dta$ID[df_dta$ID != df_dta$DISEASE]
df_dta$DISEASE[df_dta$ID != df_dta$DISEASE]

# remove column
df_dta$DISEASE <- NULL
head(df_dta)
```

This is the exact same variable as ID, so can be removed.

### Disease subtype
```{r}
# convert to factor
typeof(df_dta$DISEASE_SUBTYPE)
df_dta$fDISEASE_SUBTYPE <- as.factor(df_dta$DISEASE_SUBTYPE)

# levels
table(df_dta$fDISEASE_SUBTYPE)

# na values
sum(is.na(df_dta$fDISEASE_SUBTYPE))

sum(!is.na(df_dta$fDISEASE_SUBTYPE) & df_dta$fID == "Crohns Disease")
sum(!is.na(df_dta$fDISEASE_SUBTYPE) & df_dta$fID == "Long COVID")
sum(!is.na(df_dta$fDISEASE_SUBTYPE) & df_dta$fID == "Malignant melanoma")
```

Is Na another level of the variable, or really just missing? If the latter, 
why is there so much missing?
-> Different levels in Melanoma that doesnt seem much reported on.

### Disease proxy
```{r}
# convert to factor
typeof(df_dta$DISEASE_PROXY)
df_dta$fDISEASE_PROXY <- as.factor(df_dta$DISEASE_PROXY)

# levels
table(df_dta$fDISEASE_PROXY)

# na values
sum(is.na(df_dta$fDISEASE_PROXY))

sum(!is.na(df_dta$DISEASE_PROXY) & df_dta$fID == "Crohns Disease")
sum(!is.na(df_dta$DISEASE_PROXY) & df_dta$fID == "Long COVID")
sum(!is.na(df_dta$DISEASE_PROXY) & df_dta$fID == "Malignant melanoma")

# check where different proxies are used
crossTable_diseaseProxy <- table(df_dta$fID, df_dta$fDISEASE_PROXY)
crossTable_diseaseProxy_df <- as.data.frame.matrix(crossTable_diseaseProxy)
kable(crossTable_diseaseProxy_df, caption = "Cross Table of fID and fDISEASE_PROXY")
```

fDISEASE_PROXY: This column likely represents a related or associated condition 
for the main disease in the fID column. It might indicate conditions that are 
often seen together, risk factors, or proxy measures for broader disease 
categories.

Also a variable that is not frequently reported upon, and divides the disease in
different categories.


### Country
```{r}
# levels
table(df_dta$COUNTRY)

# na values
sum(is.na(df_dta$COUNTRY))
```
In each row the value is the same, so the variable is not necessary for
clustering. Just mention in thesis that it's data from Belgium.


### Country proxy
```{r}
# levels
table(df_dta$COUNTRY_PROXY)

# na values
sum(is.na(df_dta$COUNTRY_PROXY))
```


### Year
```{r}
# levels
table(df_dta$YEAR)
```


### Sex
```{r}
table(df_dta$SEX)
```





### Dimension
```{r}
# convert to factor
unique(df_dta$DIMENSION)
typeof(df_dta$DIMENSION)
df_dta$fDIMENSION <- as.factor(df_dta$DIMENSION)

# levels
table(df_dta$fDIMENSION)

# na values
sum(is.na(df_dta$fDIMENSION))
```
