
### ID
```{r}
# convert to factor
typeof(df_dta$ID)
df_dta$fID <- as.factor(df_dta$ID)
df_dta <- df_dta %>% relocate(fID, .after = ID)
df_dta$ID <- NULL

# levels
table(df_dta$fID)

# na values
sum(is.na(df_dta$fID))
```
This variable partitions all data points into the disease they belong to:

* **Chrons Disease:** A type of inflammatory bowel disease (IBD) that causes chronic inflammation of the digestive tract.
* **Long COVID:** (also called post-COVID syndrome) Refers to ongoing symptoms that persist for weeks or months after recovering from a COVID-19 infection.
* **Malignant melanoma:** The most serious type of skin cancer that develops in the melanocytes, the cells that produce melanin (the pigment that gives skin its color).

All rows have an id, so no cleaning needs to be done yet on the basis of this variable.
Determine urgency for every ID separately or together?


### Disease
```{r}
# convert to factor
typeof(df_dta$DISEASE)

# levels
table(df_dta$DISEASE)
df_dta$fID[as.character(df_dta$fID) != df_dta$DISEASE]
df_dta$DISEASE[as.character(df_dta$fID) != df_dta$DISEASE]

# remove column
df_dta$DISEASE <- NULL
```
This is the exact same variable as ID, so the column can be removed.


### Disease subtype
```{r}
# convert to factor
typeof(df_dta$DISEASE_SUBTYPE)
df_dta$fDISEASE_SUBTYPE <- as.factor(df_dta$DISEASE_SUBTYPE)
df_dta <- df_dta %>% relocate(fDISEASE_SUBTYPE, .after = DISEASE_SUBTYPE)
df_dta$DISEASE_SUBTYPE <- NULL

# levels
table(df_dta$fDISEASE_SUBTYPE)

# na values
sum(is.na(df_dta$fDISEASE_SUBTYPE))
```
This variable reports on different subtypes within a disease. It seems little reported on, so this is probably not useful for the priority system.


### Disease proxy
```{r}
# convert to factor
typeof(df_dta$DISEASE_PROXY)
df_dta$fDISEASE_PROXY <- as.factor(df_dta$DISEASE_PROXY)
df_dta <- df_dta %>% relocate(fDISEASE_PROXY, .after = DISEASE_PROXY)
df_dta$DISEASE_PROXY <- NULL

# levels
table(df_dta$fDISEASE_PROXY)

# na values
sum(is.na(df_dta$fDISEASE_PROXY))
```
This variable does not seem useful, as Crohn's disease is a subtype of IBD.
Malgnant melanoma is a type of skin cancer, therefore *Malignant melanoma*, *Malignant melanoma of skin* and *skin cancer* are all the same thing under the disease *Malignant melanoma*.


### Country
```{r}
# levels
table(df_dta$COUNTRY)

# na values
sum(is.na(df_dta$COUNTRY))

# remove column
df_dta$COUNTRY <- NULL
```
In each row the value is the same without missing values. 
We will remove the column here and just mention in the data-section of the thesis that the data is all obtained from Belgium.


### Country proxy
```{r}
# levels
table(df_dta$COUNTRY_PROXY)

# na values
sum(is.na(df_dta$COUNTRY_PROXY))
```
This variable has only a few variables, but will be left in the dataset because it does show distinction between datapoints
The na-values may just be an indicator that the data is obtained from Belgium.


### Year
```{r}
# levels
table(df_dta$YEAR)

# na values
sum(is.na(df_dta$YEAR))

# correct column
df_dta$YEAR[df_dta$YEAR == 2034] = 2024
table(df_dta$YEAR)

# histogram
hist(df_dta$YEAR)
```
Two rows have the year 2034. This is probably a typo for 2024.
The one datapoint from 2014 is weird, but not impossible, and not improbable enough to remove.


### Sex
```{r}
# levels
table(df_dta$SEX)

# na values
sum(is.na(df_dta$SEX))

# remove column
df_dta$SEX <- NULL
```
This variable does not give us any information about the sex. It is the same value for all rows, without missing values.
This can be safely removed.


### AGE
```{r}
# levels
table(df_dta$AGE)

# na values
sum(is.na(df_dta$AGE))

# remove column
df_dta$AGE <- NULL
```
This has the same issue as **SEX**, so the column can be removed.


### SES
```{r}
# levels
table(df_dta$SES)

# na values
sum(is.na(df_dta$SES))

# remove column
df_dta$SES <- NULL
```
Again the same issue.


### Dimension
```{r}
# convert to factor
typeof(df_dta$DIMENSION)
df_dta$fDIMENSION <- as.factor(df_dta$DIMENSION)
df_dta <- df_dta %>% relocate(fDIMENSION, .after = DIMENSION)
df_dta$DIMENSION <- NULL

# levels
table(df_dta$fDIMENSION)

# na values
sum(is.na(df_dta$fDIMENSION))
```
The dimension of the criteria, meaning what part it applies to.


### Domain
```{r}
# convert to factor
typeof(df_dta$DOMAIN)
df_dta$fDOMAIN <- as.factor(df_dta$DOMAIN)
df_dta <- df_dta %>% relocate(fDOMAIN, .after = DOMAIN)
df_dta$DOMAIN <- NULL

# levels
table(df_dta$fDOMAIN)

# na values
sum(is.na(df_dta$fDOMAIN))
```
This variable serves a similar purpose as **DIMENSION**. It separates the criteria in various categories to which they apply.


### Criterion
```{r}
# convert to factor
df_dta$fCRITERION <- as.factor(df_dta$CRITERION)
df_dta <- df_dta %>% relocate(fCRITERION, .after = CRITERION)
df_dta$CRITERION <- NULL

# levels
criterion_table <- as.data.frame(table(df_dta$fCRITERION))
kable(criterion_table, format = "markdown")

# na values
sum(is.na(df_dta$fCRITERION))
df_dta[is.na(df_dta$fCRITERION), ]

# remove row
df_dta <- df_dta[!is.na(df_dta$fCRITERION), ]
```
These are the criteria we need to label in this thesis.
Due to this missing value, this is a row we should delete, as **CRITERION** is what we need to label.
For this data point there is no **VALUE**, **KEYPOINT** or **QUOTE** either. Further indicating that this row cannot be used.


### Indicator
```{r}
# convert to factor
df_dta$fINDICATOR <- as.factor(df_dta$INDICATOR)
df_dta <- df_dta %>% relocate(fINDICATOR, .after = INDICATOR)
df_dta$INDICATOR <- NULL

# levels
indicator_table <- as.data.frame(table(df_dta$fINDICATOR))
kable(indicator_table, format = "markdown")

# na values
sum(is.na(df_dta$fINDICATOR))
```
All rows have an indicator. This variable gives for each criterion certain indicators.


### Indicator proxy
```{r}
# levels
table(df_dta$INDICATOR_PROXY)

# na values
sum(is.na(df_dta$INDICATOR_PROXY))
```
This does not tell us a lot, the variable will be left in the table, but likely won't be used.


### Measure
```{r}
# levels
table <- as.data.frame(table(df_dta$MEASURE))
kable(table, format = "markdown")

# na values
sum(is.na(df_dta$MEASURE))
```
These are the measures by which a category is portrayed. A lot of the rows do not have measures, but these may still be useful.

### Unit
```{r}
# levels
table <- as.data.frame(table(df_dta$UNIT))
kable(table, format = "markdown")

# na values
sum(is.na(df_dta$UNIT))
```
These are the units for each measure.


### Categories
```{r}
# levels
table <- as.data.frame(table(df_dta$CATEGORIES))
kable(table, format = "markdown")

# na values
sum(is.na(df_dta$CATEGORIES))
```
For each indicator there are various categories. The value for each category is regulated by a measure and unit for the measure.


### Value 
```{r}
# na values
sum(is.na(df_dta$VALUE))

# value is a character var
typeof(df_dta$VALUE)
df_dta$VALUE[!is.na(df_dta$VALUE) & is.na(suppressWarnings(as.numeric(df_dta$VALUE)))]

# convert to numeric and add extra column for non numeric to not lose data
df_dta$VALUE_num <- suppressWarnings(as.numeric(df_dta$VALUE))
df_dta$VALUE_char <- ifelse(is.na(df_dta$VALUE_num) & !is.na(df_dta$VALUE), df_dta$VALUE, NA)
df_dta <- df_dta %>% relocate(VALUE_num, .after = VALUE)
df_dta <- df_dta %>% relocate(VALUE_char, .after = VALUE_num)

df_dta[, c("VALUE_num", "VALUE_char")]

# analysis
hist(df_dta$VALUE_num, breaks = 10)
```
There are both numerical and plain text values, we separate them so we can work with both.
In the histogram it is apparent that these values are not on the same scale, they should be scaled so different values on different scales can be compared.


### SD
```{r}
hist(df_dta$SD, breaks = 10)

# na values
sum(is.na(df_dta$SD))
```
This variable is not often reported upon and can probably not be used for our purposes either.


### Lower CI
```{r}
hist(df_dta$`LOWER CI`, breaks = 10)

# na values
sum(is.na(df_dta$`LOWER CI`))
```


### Upper CI
```{r}
hist(df_dta$`UPPER CI`, breaks = 10)

# na values
sum(is.na(df_dta$`UPPER CI`))
```
These two variables follow the same analysis as **SD**.

### Source
```{r}
table(df_dta$SOURCE)

# na values
sum(is.na(df_dta$SOURCE))
```
This contains the source for the datapoints.

### Rating
```{r}
# non na values
sum(!is.na(df_dta$RATING))

# na values
sum(is.na(df_dta$RATING))

# no values so column can be removed
df_dta$RATING <- NULL
```
This variable contains no data, so it can be safely removed.

### Key points
```{r}
head(df_dta[!is.na(df_dta$KEY_POINT), "KEY_POINT"])

# na values
sum(is.na(df_dta$KEY_POINT))
```
A lot of missing values so we need to have a system where rows without keypoints do not
necessarily gets a lower score.
This variable needs to stay in plain text for classifying it with NLP.


### Quotes
```{r}
head(df_dta[!is.na(df_dta$QUOTES), "QUOTES"])

# na values
sum(is.na(df_dta$QUOTES))
```
The same applies to the quotes af for the keypoints.


### Meta 1
```{r}
head(df_dta[!is.na(df_dta$META_1), "META_1"])

# na values
sum(is.na(df_dta$META_1))
```
This is extra information about datapoints that needs to be taken into account if we want to remove or alter them.


### Meta 2
```{r}
head(df_dta[!is.na(df_dta$META_2), "META_2"])

# na values
sum(is.na(df_dta$META_2))
```
The same as metadata 1.


### Meta 3
```{r}
head(df_dta[!is.na(df_dta$META_3), "META_3"])

# na values
sum(is.na(df_dta$META_3))

# remove column
df_dta$META_3 <- NULL
```
This column contains no data so it can be removed.


### Criterion 2
```{r}
head(df_dta[!is.na(df_dta$CRITERION2), "CRITERION2"])

# na values
sum(is.na(df_dta$CRITERION2))

# check similarity to criterion 1
df_dta[!is.na(df_dta$CRITERION2) & 
       as.character(df_dta$fCRITERION) != as.character(df_dta$CRITERION2), 
       c("fCRITERION", "CRITERION2")]

# remove column
df_dta$CRITERION2 <- NULL
```
This column seems to contain the exact same data as **CRITERION** except less rows are filled in.
This variable can thus be removed.


### Comments
```{r}
head(df_dta[!is.na(df_dta$COMMENTS), "COMMENTS"])

# na values
sum(is.na(df_dta$COMMENTS))
```
Like metadata, some extra information that might be usefull.


### Qualy
```{r}
head(df_dta[!is.na(df_dta$QUALY), "QUALY"])

# na values
sum(is.na(df_dta$QUALY))

# no data so remove column
df_dta$QUALY <- NULL
```
This column contains no data, so can be removed.


## Univariate conclusion
After the univariate analysis the data looks as follows:
```{r}
head(df_dta)
dim(df_dta)
```
The 16 useful variables for further analysis are:

* fID
* fDISEASE_SUBTYPE
* fDIMENSION
* fDOMAIN
* fCRITERION
* fINDICATOR
* MEASURE
* UNIT
* CATEGORIES
* VALUE_num
* VALUE_char
* KEY_POINT
* QUOTES
* META_1
* META_2
* COMMENTS

The deleted variables are:

* DISEASE
* COUNTRY
* SEX
* AGE
* SES
* META_3
* RATING
* CRITERION2

Either because they were duplicates of other columns or if they contained no, or all the same values.
The most important findings are that many of the variables are only sparsely filled in, and we identified the important variables for further analysis.

































